TBD

### 2021-03-22 outputs/paper/paper.Rmd
Edit Power Analysis

# Reference Code: https://rdrr.io/cran/pwr/man/ES.h.html
effectSize <- 2 * asin(sqrt(propNoMoneyReturned)) - 2 * asin(sqrt(proMoneyReturned))

### Two-sample test for proportions (Unequal sample sizes)
# Reference Code:https://cran.r-project.org/web/packages/pwr/vignettes/pwr-vignette.html
# Reference: Conventional effect size from Cohen (1982)
pwr.2p.test(h = effectSize, sig.level = 0.05, power = 0.8)
```

>>>>

# Reference Code: https://rdrr.io/cran/pwr/man/ES.h.html
effectSize <- 2 * asin(sqrt(proMoneyReturned)) - 2 * asin(sqrt(propNoMoneyReturned))

### Two-sample test for proportions (Unequal sample sizes)
# Reference Code:https://cran.r-project.org/web/packages/pwr/pwr.pdf
# Reference: Conventional effect size from Cohen (1982)
pwr.2p.test(h = effectSize, sig.level = 0.05, power = 0.8)
```
